% resume.tex
% vim:set ft=tex spell:

% Global configuration
\documentclass[12pt,letterpaper]{article}
\usepackage[letterpaper,margin=.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[urw-garamond]{mathdesign}
\usepackage{mdwlist}
\usepackage{textcomp}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% Manually indent a section of text
\newenvironment{indentedsection}[1]
{\begin{list}{}
  {\setlength{\leftmargin}{#1}}
  \item[]
}
{\end{list}}

% Left/right floated/aligned columns
\newcommand{\floatcols}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  #1 &
  #2 \\
\end{tabular*}}

% Same, but for the title
\newcommand{\headercols}[3]
{\begin{tabular*}{\linewidth}{l c r}
  #1 &
  #2 &
  #3 \\
\end{tabular*}}

% Holy cow, the word 'C++' is SO UGLY WITHOUT THIS
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% Actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Dan Poggi}}

dan@danpoggi.com\ \ \textbullet
\ \ (616)~425-9376
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
  \parskip=0.1em

  \item 
    \floatcols
      {\textbf{Michigan State University}}
      {\textbf{East Lansing, Mich.}}
    \\
    \floatcols
      {\emph{B.S.~Computer Science, Cognate in Business}}
      {\emph{September 2009 -- Present}}
\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Work Experience}

\begin{itemize}
  \parskip=0.1em

  \item
    \floatcols
      {\textbf{Olark}}
      {\textbf{Ann Arbor, Mich. and Palo Alto, Calif.}}
    \\
    \floatcols
      {\emph{Frontend/Backend Development Intern}}
      {\emph{June 2011 -- November 2011}}
    \begin{itemize*}
      \item Worked on implementing best practices in Olark's Rails frontend.
      \item Developed server deployment procedures for scaling Olark's backend services in the cloud.
    \end{itemize*}

  \item
    \floatcols
      {\textbf{Michigan State University Physical Plant}}
      {\textbf{East Lansing, Mich.}}
    \\
    \floatcols
      {\emph{Computer Support Technician}}
      {\emph{March 2010 -- June 2011}}
    \begin{itemize*}
      \item Responsible, along with a team of 12, for the maintenance,
      support, and growth of a network serving over 1,000 client computers.
      \item Personally tasked with updating the structure of Microsoft Access
      databases, scripting using Windows PowerShell, supporting video editing
      software, and documenting new procedures for use by computer support staff.
    \end{itemize*}

  \item
    \floatcols
      {\textbf{Self-Employed}}
      {\textbf{Grand Rapids, Mich.}}
    \\
    \floatcols
      {\emph{Web Developer \& Computer Support Technician}}
      {\emph{September 2005 -- March 2010}}
    \begin{itemize*}
      \item Employed by businesses to produce web sites and services using
      cutting-edge web technologies.
      \item Hired by personal clients to diagnose and repair computer problems
      on Windows and Macintosh operating systems, and deploy new systems
      involving computers and/or consumer electronics.
    \end{itemize*}
  
  \item
    \floatcols
      {\textbf{Grand Rapids Community College, Computer Camp for Teens}}
      {\textbf{Grand Rapids, Mich.}}
    \\
    \floatcols
      {\emph{Teaching Assistant}}
      {\emph{Summers 2005 and 2006}}
    \begin{itemize*}
      \item Used skills in HTML and Visual Basic to teach students about
      software including Microsoft Visual Basic 6 and Macromedia Dreamweaver.
      \item Worked with students aged 8-18 with various levels of technical skill.
      \item Held this position on a volunteer basis during the summers of
      2000-2004.
    \end{itemize*}
\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Technical Skills}

\begin{indentedsection}{\parindent}
  \floatcols
    {Languages:}
    {Ruby, Objective-C, C, \CPP, Python, JavaScript, PHP, C\#}
  \\[.4em]
  \floatcols
    {Libraries/Frameworks:}
    {Rails, Sinatra, Backbone.js, Cocoa, Win32~API, .NET CLR}
  \\[.4em]
  \floatcols
    {Tools:}
    {Vim, Xcode, Tmux, ZSH, Git}
  \\[.4em]
  \floatcols
    {Databases:}
    {MySQL, PostgreSQL, MongoDB, Oracle 10g}
  \\[.4em]
  \floatcols
    {Operating Systems:}
    {Mac OS X, various UNIX platforms, Windows}
\end{indentedsection}

\end{document}
